A holomorphic approach to membranes and fivebranes

### 2022-07-09 fivebranes/twisted.tex
twisted membranes

Recently in \cite{CLsugra}, Costello and Li gave a rigorous definition of twisted supergravity.
In any theory of supergravity, there is an collection of bosonic ghosts which, in part, incorporate local supersymmetry.
By definition, twisted supergravity is supergravity in the background where a bosonic ghost for supersymmetry takes a nonzero value $Q$, where $Q$ is a twisting supercharge.

@@

The fields of the theory are given by a local dg-lie algebra on $S\times Y$ whose underlying sheaf of cochain complexes is
\beqn
\cL_{5d} \define \Omega^\bu(S) \hotimes \Omega^{0,\bu}(Y) .
\eeq.

The sheaf of holomorphic functions on $Y$ has a natural lie bracket given by the holomorphic poisson bracket. This can be extended in a graded way to the entire Dolbeault complex; \cL_{5d} is then the tensor product of a commutative algebra and a lie algebra so is canonically a local dg-lie algebra.
The five-dimensional theory

@@

>>>>

Recently in \cite{CLsugra}, Costello and Li gave a rigorous definition of twisted supergravity.
In any theory of supergravity, the action of supersymmetry is gauged. When one treats the theory in the BRST formalism, the fields then include a collection of bosonic ghosts which homologically enforce invariance under the odd gauge symmetries.

By definition, twisted supergravity is supergravity in the background where a bosonic ghost for supersymmetry takes a nonzero value $Q$, where $Q$ is a twisting supercharge.

@@

The fields of the theory are given by a local dg-lie algebra on $S\times Y$ whose underlying sheaf of cochain complexes is
\beqn
\cL_{5d} \define \Omega^\bu(S) \hotimes \Omega^{0,\bu}(Y) .
\eeq

The sheaf of holomorphic functions on $Y$ has a natural lie bracket given by the holomorphic poisson bracket $\{-,-\}_{Y}$. This can be extended in a graded way to the entire Dolbeault complex; $\cL_{5d}$ is then the tensor product of a commutative algebra and a lie algebra so is canonically a local dg-lie algebra.

Wedging and integrating against the holomorphic volume form on $Y$ defines an odd pairing on $\cL_{5d}$; together with the above, this equips $\cL_{5d}$ with the structure of a $\Z/2$-graded BV theory.

The equations of motion of $\cL_{5d}$ describe locally-constant families of deformations of the fixed holomorphic Poisson structure on $Y$.

@@

\subsection{Twisted membranes}

The theory on a stack of $N$ membranes probing the origin in $\C^{4}/\Z_{k}$ is expected to be described by the ABJM theory - a 3d $\cN=6$ superconformal gauge theory with gauge group $U(N)\times U(N)$ at levels $\pm k$ respectively \cite{} For $k=1,2$ the theory witnesses an enhancement to $\cN=8$ due to a nonperturbative effect. \cite{}

Twists of $\cN=8$ gauge theories in 3d were classified in \cite{}. Moreover, the ABJM theories are examples of 3d $\cN=2$ Chern-Simons matter theories, whose twists were studied in \cite{}. Twists of such occur in two inequivalent classes, similarly labeled by the dimension of the subspace of translations given by the image of the twisting supercharge:

\begin{itemize}
  \item The minimal twist. This twist leaves 2 real directions invariant. The theory can be defined on a 3-manifold of the form $S\times \Sigma$ where $S$ is a smooth oriented one-manifold and $\Sigma$ is a Riemann surface equipped with a fourth-root of its canonical bundle.

  \item The nonminimal twists. There are two such twists, both of which leave 3 real directions invariant, and are permuted under 3d mirror symmetry.
\end{itemize}

\parsec

We briefly recall the description of the minimal twist of the ABJM theory for $N=1$.

\surya{fields, gauge symmetries, etc}

In the BV formalism, this free theory can be packaged into the data of an abelian $\Z$ graded local Lie algebra on $\Sigma$ which takes the form
\[
\Omega^{\bu}(S)\times \left (\Omega^{0,\bu}(\Sigma) \oplus \Pi \Omega^{0,\bu} (\Sigma )\right ) \otimes \C^{4}.
\]
